---
title: "Prioritising doses to at risk groups results"
author: "GMB"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=10000); require(ggpubr); require(knitr)

list_poss_Rdata = list.files(path="x_results/",pattern = "FleetMedic_run_*")
list_poss_Rdata_details = double()
for (i in 1:length(list_poss_Rdata)){
  list_poss_Rdata_details = rbind(list_poss_Rdata_details,
                                 file.info(paste('x_results/',list_poss_Rdata[[i]],sep=''))$mtime)
}
latest_file = list_poss_Rdata[[which.max(list_poss_Rdata_details)]]

load(paste('x_results/',latest_file,sep=''))
```

# Introduction
Note: This document includes results for the prioritisation of  **`r paste(risk_group_name)`**.

## Overarching assumptions

Variable | Value | Source
---------|--------|--------
Circulating strain | `r paste(strain_inital)`|
Delivery of doses post outbreak | `r paste(outbreak_post_rollout)`|
Length of model run | `r paste(model_weeks)`|
Current vaccine coverage | dose one: `r paste(round(current_coverage[1]),'%',sep='')`; dose two: `r paste(round(current_coverage[2]),'%',sep='')`| John Hopkins COVID-19 vaccination data
Current vaccine coverage target | `r paste(gov_target*100,'%',sep='')` | Government target in COVAX documentation May 2021
Proportion of population willing to be vaccinated (general population) | `r paste(vax_strategy_toggles_CURRENT_TARGET$vax_strategy_max_expected_cov*100,'%',sep='')`|Survey estimating vaccine acceptance in January 2021 (Solis et al., 2021)
Daily capacity for vaccination (doses) | `r paste(vax_strategy_toggles_CURRENT_TARGET$vax_strategy_roll_out_speed)` | Slightly lower than the pilot vaccination campaign October-November 2021 
Anticipated type of future vaccine doses| `r paste(vax_strategy_toggles_CURRENT_TARGET$vax_strategy_vaccine_type)` | The Government of Sierra Leone has demonstrated a strong preference for this vaccine, negotiating with major donors, such as the Government of Italy, to change their donations of double-dose vaccines (such as Pfizer) to Janssen vaccines for ease of deployment 
Waning of VE against acquisition | `r paste(waning_toggle_acqusition)`|
Waning of VE against severe disease | `r paste(waning_toggle_severe_outcome)`|
Waning of infection-derived immunity against acquisition | `r paste(waning_toggle_rho_acqusition)`|
Waning of infection-derived immunity against severe outcomes | Not yet included |

## Risk group parameters (unless otherwsie specified):

Variable | Value | Source
---------|--------|--------
Risk group prioritisation to date| `r paste(risk_group_prioritisation_to_date)` | 
Proportion of population willing to be vaccinated (at risk group) | `r paste(vax_strategy_toggles_CURRENT_TARGET$vax_strategy_max_expected_cov*100,'%',sep='')`|
Increased risk of risk group | `r paste(RR_estimate)` | 
Default_prioritisation_proportion | `r paste(default_prioritisation_proportion)` | 

***

# Prioritising primary dose coverage by x%
```{r echo=FALSE , fig.width=10,fig.height=5}

results_warehouse_FM[[1]][[3]]
kable(results_warehouse_FM[[1]][[4]]$absolute, caption = 'Absolute difference in outcomes (compared to no prioritisation)',digits=0,format.args = list(big.mark = ","))
kable(results_warehouse_FM[[1]][[4]]$relative, caption = 'Relative difference in outcomes',digits=2) 
```

***

# Delivery of booster doses to at risk group

***

# Sensitivity analysis
## Range of possible RR
```{r echo=FALSE , fig.width=10,fig.height=5}

#results_warehouse_FM[[3]][[3]]
#kable(results_warehouse_FM[[3]][[4]]$absolute, caption = 'Absolute difference in outcomes compared to no #difference in risk (RR=1)',digits=0,format.args = list(big.mark = ","))
#kable(results_warehouse_FM[[3]][[4]]$relative, caption = 'Relative difference in outcomes',digits=2) 
```
## Reduced VE
## Altered contact patterns
## Vaccine hesitancy