---
title: "Vaccine allocation project results"
author: "GMB"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=10000); require(ggpubr)

load(paste("complete_model_run_",Sys.Date(),".Rdata",sep=''))
```
```{r echo=FALSE}
paste("Setting for this run is: ",setting)

```


## Introduction

This document brings together results from multiple model runs. It is intended to be re-run as the model is updated.

### Target questions
* What impact will the existing vaccination plan have on morbidity and mortality?
* What impact can be achieved under different levels of vaccine coverage?
* What are the potential benefits of expanding the immunisation schedule to include children?

### Overarching assumptions
Unless otherwise specified, key model assumptions in this run are:  

Variable | Value
---------|--------
Circulating strain | `r paste(strain_inital)`
Length of model run | `r paste(model_weeks)`
Proportion of population willing to be vaccinated | `r paste(vax_strategy_toggles$vax_strategy_max_expected_cov)`
Daily capacity for vaccination (doses) | `r paste(vax_strategy_toggles$vax_strategy_roll_out_speed)`
Vaccine type used| `r paste(vax_strategy_toggles$vax_strategy_vaccine_type)`

### Next steps for noting
* update of infection- and vaccine-derived immunity

### Layout of results
1. Impact of current program targets
    + roll-out prior to outbreak
    + roll-out during an outbreak
2. Varying levels of coverage
    + using current age-specific eligiblity
    + expanding eligibility to children
3. Varying speed of vaccine roll-out
4. Other sensitivity analysis
    + turning on/off waning of vaccine-derived immunity
    + simulating outbreaks of different strains
    + experimenting with different age-prioritisation strategies
    
***
  
## (1/4) Impact of current program targets
#### (A/B) Roll-out prior to outbreak
#### (B/B) Roll-out during an outbreak

***

## (2/4) Varying levels of coverage
#### (A/B) Using current age-specific eligiblity
#### (B/B) Expanding eligibility to children

***

## (3/4) Varying speed of vaccine roll-out
This section models varying speeds of vaccine roll-out *DURING* an outbreak.

***

## (4/4) Other sensitivity analysis
#### (A/C) Turning on/off waning of vaccine-derived immunity
#### (B/C) Simulating outbreaks of different strains
#### (C/C) Experimenting with different age-prioritisation strategies

***






```{r cars}

summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
